Predicting Severity of _C. difficile_ Infections from the Taxonomic Composition of the Gut Microbiome

### 2023-06-08 paper/paper.qmd
Add funding statement
Trim trailing whitespace
Need schtools & glue to render
Fix typo

  We then trained ML models to predict CDI severity on OTU relative abundances

@@

knitr::opts_chunk$set(dpi = 600)
knitr::knit_hooks$set(inline = schtools::inline_hook)

@@

>>>>

  We trained ML models to predict CDI severity on OTU relative abundances

@@

schtools::set_knitr_opts()

@@

The funders had no role in study design, data
collection and interpretation, or the decision to submit the work for
publication.
